On the Cram\'{e}r-Rao bound for polynomial phase signals

### 2013-02-08 paper.tex

%\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
\documentclass[journal,10pt]{IEEEtran}

@@

\author{Robby McKilliam and Andr\'{e} Pollok%
\thanks{Supported under the Australian Government's Australian Space Research Program.
Robby McKilliam and Andr\'{e} Pollok are with the Institute for Telecommunications Research, The University of South Australia, SA, 5095}
}
% The paper headers
\markboth{Robby McKilliam and Andre Pollock, On the Cram\'{e}r-Rao bound for polynomial phase signals}%
{DRAFT \today}

% make the title area
\maketitle

\begin{abstract}
Polynomial-phase signals have applications including radar, sonar, geophysics, and radio communication.  Of practical importance is the estimation of the parameters of a polynomial phase signal from a sequence of noisy observations.  
%Assuming that the noise is additive and Gaussian,  Peleg and Porat approximated the Cram\'{e}r-Rao bound for this estimation problem.  The approximation is accurate when the number of observations is sufficiently larger than the order of the polynomial phase signal.  
We derive closed form and numerically stable formulae for the Cram\'{e}r-Rao  lower bounds of these parameters under the assumption that the noise is additive white and Gaussian.  This is achieved by making use of a family of orthogonal polynomials.
\end{abstract}

\begin{IEEEkeywords}
Polynomial-phase signals, Cram\'{e}r-Rao bound.
\end{IEEEkeywords}

@@

The paper is organised as follows.  In Section~\ref{sec_crb} we derive the Fisher information matrix in a similar way to Peleg and Porat~\cite{Peleg1991_CRB_PPS_1991}.  The matrix can be poorly conditioned and in this case inverting it to obtain the Cram\'{e}r-Rao bound is difficult.  In Section~\ref{sec:changing-basis} we describe some general results regarding changing the basis in which a polynomial phase signal may be represented.  We describe the Fisher information matrix corresponding with a chosen basis, and relate the matrices between two bases.  In Section~\ref{sec:discr-orth-polyn} we introduce a family of discrete orthogonal polynomials.  By transforming into this basis, the corresponding Fisher information matrix becomes diagonal, making matrix inversion simple.  This leads directly to closed form expressions for the Cram\'{e}r-Rao bounds.  In Section~\ref{sec:stab-cons} we manipulate these expression so as to make their numerical stability clear.  This simultaneously indicates the prefered stable approach to implementing the formula in a digital computer.  To keep our derivation simple we initially assume that the amplitude and the noise variance are fixed constants, and not parameters to be estimated.  However, including the amplitude and noise variance is straightforward, and we do this in Section~\ref{sec:including-amplitude}.  
Section~\ref{sec:simuations} SIMS BLERG.

>>>>

%\documentclass[preprint,10pt]{elsarticle}
%\documentclass[review]{elsarticle}
\documentclass[5p]{elsarticle}

@@

\author{Robby McKilliam} 
\author{Andr\'{e} Pollok}
\address{Institute for Telecommunications Research, The University of South Australia, SA, 5095}
\fntext[asrp]{Supported under the Australian Government's Australian Space Research Program.}

\begin{abstract}
Polynomial-phase signals have applications including radar, sonar, geophysics, and radio communication.  Of practical importance is the estimation of the parameters of a polynomial phase signal from a sequence of noisy observations.  Assuming that the noise is additive and Gaussian, the direct evaluation of the Cram\'{e}r-Rao lower bound for this estimation problem involves evaluating the inverse of a matrix.  Computing this inverse is numerically difficult for polynomial phase signal of large order.  By making use of a family of orthogonal polynomials, we derive formulae for the Cram\'{e}r-Rao lower bounds that are numerically stable and easy to compute.
\end{abstract}

\begin{keyword}
Polynomial-phase signals, Cram\'{e}r-Rao bound.
\end{keyword}

\end{frontmatter}

@@

The paper is organised as follows.  In Section~\ref{sec_crb} we derive the Fisher information matrix in a similar way to Peleg and Porat~\cite{Peleg1991_CRB_PPS_1991}.  The matrix can be poorly conditioned and in this case inverting it to obtain the Cram\'{e}r-Rao bound is difficult.  In Section~\ref{sec:changing-basis} we describe some general results regarding changing the basis in which a polynomial phase signal may be represented.  We describe the Fisher information matrix corresponding with a chosen basis, and relate the matrices between two bases.  In Section~\ref{sec:discr-orth-polyn} we introduce a family of discrete orthogonal polynomials.  By transforming into this basis, the corresponding Fisher information matrix becomes diagonal, making matrix inversion simple.  This leads directly to closed form expressions for the Cram\'{e}r-Rao bounds.  %In Section~\ref{sec:stab-cons} we manipulate these expression so as to make their numerical stability clear.  This simultaneously indicates the prefered stable approach to implementing the formula in a digital computer.  
To keep our derivation simple we initially assume that the amplitude and the noise variance are fixed constants, and not parameters to be estimated.  However, including the amplitude and noise variance is straightforward, and we do this in Section~\ref{sec:including-amplitude}.  
Section~\ref{sec:simuations} %SIMS BLERG.
